Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2022-11-22 reports/supplement/supplement_0.9.1.Rmd
update supplement

The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth5) show the effects of diversity with long to shorter wait times.

@@

When there was medium to high variation in only the phototrophic sulfur bacteria (PB), the strain dynamics deviated from the standard pattern: at low oxygen diffusivity, all three functional groups coexisted. Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse at medium oxygen diffusivity (medium variation in PB, Figure xy) or never collapsed (high variation in PB, Figure xy). On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state.

The same pattern occurred for medium to high simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure xy). On the trajectory of decreasing oxygen diffusivity, cyanobacteria dominated over the entire gradient of oxygen diffusivity, such that effects of PB diversity did not play out on this trajectory.

The reason for coexistence of all three groups at low oxygen diffusivity was that the PB strain that dominated at low oxygen diffusivity (the least tolerant strain) lowered the sulfide concentrations to such low levels that cyanobacteria were able to grow. The higher the trait variation in PB, the higher the intrinsic growth rate of the least tolerant PB strain, and the higher its consumption of sulfide. Consequently, moderate variation in PB lowered the sulfide concentration such that the tipping point from anoxic to oxic occurred earlier (as discussed in the previous section), and medium to high variation in PB lowered the sulfide concentration even further such that cyanobacteria were able to grow and coexist with the two groups of sulfur bacteria at low oxygen diffusivity.

At intermediate levels of oxygen diffusivities, the cyanobacteria were usually excluded (Figure xy). We speculate that this might be associated with the increase in sulfide prior to the collapse of the phototrophic sulfur bacteria. This increase in sulfide occurred simultaneously with turnover to PB strains with lower intrinsic growth rate and with a decline in PB density; these two processes likely resulted in less consumption of sulfide.

Owen, please add here 3 figures that match the text above:

```{r}
nine_strains <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method", 
                         "event_definition_2",
                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

(1) medium variation in only PB showing coexistence of all groups at low ox diff,

nine_strain_one <- filter(nine_strains,
       CB_var_gmax_s == 0,
       SB_var_gmax_s == 0,
       abs(PB_var_gmax_s - 0.064819946) < 0.001)

parameter <- nine_strain_one$parameter[[1]]
parameter$strain_parameter <- nine_strain_one$pars[[1]]
#parameter$strain_parameter <- ss_result$pars[[1]]
total_initial_abundances <- 10^5
parameter <- set_temporal_ssfind_initial_state(parameter,
                                               total_initial_abundances,
                                               total_initial_abundances,
                                               total_initial_abundances)
parameter$log10a_series <- c(-7, -7)
wait_time <-  1e5
parameter$sim_duration <- wait_time * length(parameter$log10a_series)
parameter$sim_sample_interval <- 10
#parameter$sim_duration
test1 <- run_simulation(parameter)

(ref:PB-dyn1) Temporal dynamics of an ecosystem with a , the same one as in Figure \@ref(fig:max-tol3) simulated with constant $log_{10}$ oxygen diffusivity of -7.

```{r PB-dyn1, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-dyn1)', fig.height=10, fig.width=8, fig.align="center"}
p <- plot_dynamics(test1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[4]]$data <- p[[4]]$data %>% 
  dplyr::filter(species != "a")
p[[4]]$data$species <- p[[4]]$data$species %>%
  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
p[[4]] <- p[[4]] + 
  xlab("time (h)") + 
  ylab(expression(log[10](concentration)~(µM))) + 
  labs(colour = "substrate") +
  theme_bw()

(2) high variation in only PB showing coexistence of all groups at low ox diff and CB never collapsing on the decreasing ox diff trajectory,

(3) high variation in both CB and PB.

@@

In the main text we show that trait variation can affect resilience. In this supplementary section, we discuss the mechanism(s) underlying the observed diversity effects. We first explain the two major classes of mechanisms known to drive diversity effects, and then use additional simulations to elucidate the mechanisms operating in our study.

@@

Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001). The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, i.e. the diversity effect is driven by only one (or few) species (Cardinale et al. 2011). In contrast, the complementarity effect occurs when higher ecosystem functioning in more diverse communities is due to niche differences or positive interactions among species, i.e. the diversity effect is driven by many species (Cardinale et al. 2011). Both effects are considered valid and important mechanisms by which diversity affects ecosystem functioning (Cardinale et al. 2006, 2011, 2012; Fargione et al. 2007).

@@

We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain or if other strains played a role as well. To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance (which also necessarily had the lowest maximum growth rate). That is, rather than increasing diversity we only increased tolerance of a single strain. Specifically, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation. We also manipulated in which of the functional groups tolerance increased. For example, in a simulation to be compared with variation in only the SB group (and no variation in the CB or PB groups), the SB group contained the strain with highest tolerance, whereas CB and PB each contained the strain with mean tolerance. We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text. In addition, we compared the strain dynamics across the oxygen diffusivity gradient of the tolerance manipulation and the diversity manipulation. If the observed diversity effects are caused by the sampling effect, we expect there to be no difference between the tolerance manipulation and the diversity manipulation.

We found no difference between the diversity and the tolerance manipulation when trait values were low (Figure \@ref(fig:max-tol1)). When trait values were medium to high, however, we did find differences between the diversity and tolerance manipulation for most combinations except for diversity/tolerance in only CB and in SB-PB (Figure \@ref(fig:max-tol1)). We describe and discuss these differences in detail in the sections below. Briefly, in these scenarios less tolerant strains did play a role because of their high intrinsic growth rates. Specifically, absence of SB strains with high growth rate led to reduced production of sulfide and therefore to coexistence with cyanobacteria at low oxygen diffusivity. In contrast, absence of PB strains with high growth rate led to reduced consumption of sulfide and therefore precluded coexistence with cyanobacteria at low oxygen diffusivity (as observed when there was high variation in PB).

@@

When SB contained multiple strains varying in growth rate (and tolerance) there were only two stable states (Figure \@ref(fig:max-tol2)), as was previously reported. When, however, only one SB strain with very high tolerance and low maximum growth rate was present, there were three stable states: the two previously found, and another state at low oxygen diffusivity where all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple SB strains varying in tolerance.

Apparently, at low oxygen diffusivity levels, the absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria. The most tolerant SB strain has a low intrinsic growth rate, which leads to less production of sulfide. Presence of only the most tolerant SB strain therefore results in lower sulfide concentrations (Figure \@ref(fig:max-tol2) vs Figure \@ref(fig:max-tol3)), allowing growth of cyanobacteria at low oxygen diffusivity.

However, cyanobacteria are excluded at intermediate oxygen diffusivity. We speculate that this might be associated with the increase in sulfide at intermediate oxygen diffusivity, which might be due to the decline and collapse of PB and therefore reduced consumption of sulfide.   
(ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).

@@

In the SB-CB case, presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure xy) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)). As discussed in the previous section, the low intrinsic growth rate of the most tolerant SB strain led to less production of sulfide such that SB could not exclude CB.

Owen please add here a figure for medium trait values for the SB-CB case (only most tolerant strain), showing coexistence of all three groups at low ox diff.

@@

Whereas medium to high diversity in only PB led to three states including one with coexistence of all three functional groups (Figure xy), presence of only the most tolerant PB strain led to only two stable states, namely the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure xy). The most tolerant PB strain has a low intrinsic growth rate, leading to less consumption of sulfide and therefore to higher sulfide concentrations compared to a system that contains both slow- and fast-growing strains. Due to the higher sulfide concentrations in the system with only the most tolerant PB strain, cyanobacteria were not able to grow at low oxygen diffusivity levels.

For the same reasons we found three states on the trajectory of increasing oxygen diffusivity for medium to high simultaneous trait variation in PB and CB but not for the corresponding tolerance manipulation (data not shown).

Owen please add here two figures:
(1) One for high trait variation in only PB showing coexistence of all three groups.
(2) One for high tolerance in only PB (corresponding in trait values to the figure before) showing standard dynamics.

@@

At high levels of diversity vs. tolerance, resilience of the oxic state is greater when in each of the three functional groups only the most tolerant strain is present rather than when there is variation in strain tolerance within groups. It is not entirely clear why this effect occurs only in this combination.

>>>>

The following figures \@ref(fig:div-temp-meth1)-\@ref(fig:div-temp-meth4) show the effects of diversity with long to shorter wait times.

@@

When there was medium to high variation in only the phototrophic sulfur bacteria (PB), the strain dynamics deviated from the standard pattern: at low oxygen diffusivity, all three functional groups coexisted. Specifically, on the trajectory of decreasing oxygen diffusivity, cyanobacteria reappeared at low oxygen diffusivity after their collapse (Figure \@ref(fig:PB-stabstat1)) or never fully collapsed (high variation in PB, Figure \@ref(fig:PB-stabstat2)). On the trajectory of increasing oxygen diffusivity, cyanobacteria coexisted with the two groups of sulfur bacteria at low oxygen diffusivity, collapsed at medium levels of oxygen diffusivity, and then increased to sole dominance at the tipping point to the oxic state (Figure \@ref(fig:PB-stabstat1)).

The same pattern occurred for medium to high simultaneous variation in phototrophic sulfur bacteria and cyanobacteria, albeit only on the trajectory of increasing oxygen diffusivity (Figure \@ref(fig:CBPB-stabstat3)). On the trajectory of decreasing oxygen diffusivity, cyanobacteria dominated over the entire gradient of oxygen diffusivity, such that effects of PB diversity did not play out on this trajectory.

The reason for coexistence of all three groups at low oxygen diffusivity is likely that the PB strain that dominated at low oxygen diffusivity (the least tolerant strain) lowered the sulfide concentrations to such low levels that cyanobacteria were able to grow. The higher the trait variation in PB, the higher the maximum growth rate of the least tolerant PB strain, and the higher its consumption of sulfide. Consequently, moderate variation in PB lowered the sulfide concentration such that the tipping point from anoxic to oxic occurred earlier (as discussed in the previous section), and medium to high variation in PB lowered the sulfide concentration even further such that cyanobacteria were able to grow and coexist with the two groups of sulfur bacteria at low oxygen diffusivity.

At intermediate levels of oxygen diffusivities, the cyanobacteria were excluded (Figure \@ref(fig:PB-stabstat1)). We speculate that this might be associated with the increase in sulfide prior to the collapse of the phototrophic sulfur bacteria. This increase in sulfide occurred simultaneously with turnover to PB strains with lower maximum growth rate and with a decline in PB density; these two processes likely resulted in less consumption of sulfide.

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

max_CB_var_gmax <- max(ss_9s$CB_var_gmax_s)
max_SB_var_gmax <- max(ss_9s$SB_var_gmax_s)
max_PB_var_gmax <- max(ss_9s$PB_var_gmax_s)

ss_9s <- ss_9s %>%
  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
```

(ref:PB-stabstat1) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is moderate to high. This example is when the standardised amount of trait variation is 0.74 (0 being no variation, and 1 being the maximum amount in any simulation.)

```{r PB-stabstat1, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat1)', fig.height=10, fig.width=8, fig.align="center"}
this_dat <- ss_9s %>%
  filter(
    CB_var_gmax_s == 0,
    SB_var_gmax_s == 0
  )
this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
which_one <- 15
#print(paste0("Standardised level of variation = ",
#round(this_dat$standvar_PB_gmax[this_one],2)))
fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
```

(ref:PB-stabstat2) High trait variation in only the PB group results in coexistence of all groups at low oxygen diffusivity levels (as in Figure \@ref(fig:PB-stabstat1)) and also no collapse in CB abundance in the decreasing oxygen diffusivity trajectory. This example is when the standardised amount of trait variation is 0.95 (0 being no variation, and 1 being the maximum amount in any simulation.)

```{r PB-stabstat2, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat2)', fig.height=10, fig.width=8, fig.align="center"}
which_one <- 19
#print(paste0("Standardised level of variation = ",
#round(this_dat$standvar_PB_gmax[this_one],2)))
fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
```

(ref:CBPB-stabstat3) Stable states when there is high trait variation in both CB and PB groups. This example is when the standardised amount of trait variation is 0.95 (0 being no variation, and 1 being the maximum amount in any simulation.)

```{r CBPB-stabstat3, echo = FALSE,  include=TRUE, fig.cap='(ref:CBPB-stabstat3)', fig.height=10, fig.width=8, fig.align="center"}
this_dat <- ss_9s %>%
  filter(
    SB_var_gmax_s == 0,
    abs(standvar_CB_gmax - standvar_PB_gmax) < 0.00001
  )
this_dat <- this_dat[order(this_dat$CB_var_gmax_s), ]
which_one <- 19
#print(paste0("Standardised level of variation = ",
#round(this_dat$standvar_PB_gmax[this_one],2)))
fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
```

@@

In the main text we show that trait variation (functional diversity) can affect resilience. In this supplementary section, we discuss the mechanism(s) underlying the observed diversity effects. We first explain the two major classes of mechanisms known to drive diversity effects, and then use additional simulations to elucidate the mechanisms operating in our study.

@@

Research about the relationship between biodiversity and ecosystem functioning has identified two major mechanisms by which diversity affects ecosystem functioning: the selection/sampling effect and the complementarity effect (Loreau & Hector 2001). The sampling effect occurs when more diverse communities have higher functioning because they have a higher probability of containing the best-performing species, and when only one (or few) of the species in a community determine the community and ecosystem level properties, such as biomass production or stability (Cardinale et al. 2011). In contrast, the complementarity effect occurs when higher ecosystem functioning in more diverse communities is due to niche differences or positive interactions among species, i.e. the diversity effect is driven by combinations of the species in a community (Cardinale et al. 2011). Both effects are considered valid and important mechanisms by which diversity affects ecosystem functioning (Cardinale et al. 2006, 2011, 2012; Fargione et al. 2007).

@@

We investigated if the diversity effects observed in our study were in line with the sampling effect, that is, driven entirely by the presence of the most tolerant strain or if other strains played a role as well. To this end, we ran additional simulations where functional groups contained only the strain with greatest tolerance (which due to the tradeoff also had the lowest maximum growth rate). That is, rather than increasing diversity we only increased tolerance of a single strain. Specifically, for each of the 20 levels of trait variation, we made simulations where each functional group had only one strain, and its trait values corresponded with those of the most tolerant strain for the given level of trait variation. We also manipulated in which of the functional groups tolerance increased. For example, in a simulation to be compared with variation in only the SB group (and no variation in the CB or PB groups), the SB group contained the strain with highest tolerance, whereas CB and PB each contained the strain with mean tolerance. We then compared the tipping point positions resulting from this tolerance manipulation with the tipping point positions resulting from the diversity manipulation presented in the main text. In addition, we compared the strain dynamics across the oxygen diffusivity gradient of the tolerance manipulation and the diversity manipulation. If the observed diversity effects are caused by the sampling effect, we expect there to be no difference between the tolerance manipulation and the diversity manipulation.

We found no difference between the diversity and the tolerance manipulation when trait values were low (Figure \@ref(fig:max-tol1)). When trait values were medium to high, however, we did find differences between the diversity and tolerance manipulation for most combinations except for diversity/tolerance in only CB and in SB-PB (Figure \@ref(fig:max-tol1)). We describe and discuss these differences in detail in the sections below. Briefly, in these scenarios less tolerant strains did play a role because of their high maximum growth rates. Specifically, absence of SB strains with high growth rate led to reduced production of sulfide and therefore to coexistence with cyanobacteria at low oxygen diffusivity. In contrast, absence of PB strains with high growth rate led to reduced consumption of sulfide and therefore precluded coexistence with cyanobacteria at low oxygen diffusivity (as observed when there was high variation in PB).

@@

When SB contained multiple strains varying in growth rate (and tolerance) there were two stable states at intermediate levels of oxygen diffusivity, only one stable state at low oxygen diffusivity with only sulfur bacteria, and with only one stable state at high oxygen diffusivity with high cyanobacterial density (Figure \@ref(fig:max-tol2)), as was previously reported. When, however, only one SB strain with very high tolerance and low maximum growth rate was present, the stable states change: at low oxygen diffusivity  all three functional groups coexisted (Figure \@ref(fig:max-tol3)) – this never occurred when there were multiple SB strains varying in tolerance.

Apparently, at low oxygen diffusivity levels, the absence of SB strains with high growth rate precludes the formation of a stable state that does not include cyanobacteria. The most tolerant SB strain has a low maximum growth rate, which leads to less production of sulfide. Presence of only the most tolerant SB strain therefore results in lower sulfide concentrations (Figure \@ref(fig:max-tol2) vs Figure \@ref(fig:max-tol3)), allowing growth of cyanobacteria at low oxygen diffusivity.

However, cyanobacteria are excluded at intermediate oxygen diffusivity. We speculate that this might be associated with the increase in sulfide at intermediate oxygen diffusivity, which might be due to the decline and collapse of PB and therefore reduced consumption of sulfide.

(ref:max-tol2) Stable states found when there is variation among nine strains of SB and the amount of variation is high. All other aspects are the same as in Figure \@ref(fig:repl-meth2).

@@

In the SB-CB case, the presence of only the most tolerant strain led to coexistence of all groups at low levels of oxygen diffusivity when trait values were moderately high (Figure \@ref(fig:max-tol55)) or to absence of alternate stable states and sole dominance of cyanobacteria when trait values were high (Figure \@ref(fig:max-tol5)). As discussed in the previous section, the low maximum growth rate of the most tolerant SB strain led to less production of sulfide such that SB could not exclude CB.

(ref:max-tol55)  Stable states found when CB and SB each contain only the single most tolerant strain with moderate tolerance. All other aspects are the same as in Figure \@ref(fig:repl-meth2).

```{r max-tol55, echo = FALSE,  include=TRUE, fig.cap='(ref:max-tol55)', fig.height=10, fig.width=8, fig.align="center"}
#max_tol_one_CBSB <- filter(maxtolonly_strains,
#       abs(CB_var_gmax_s - 0.026592798) < 0.001,
#       abs(SB_var_gmax_s - 0.079778395) < 0.001,
#       PB_var_gmax_s == 0)
max_tol_one_CBSB <- filter(maxtolonly_strains,
       abs(CB_var_gmax_s - 0.023268699) < 0.001,
       abs(SB_var_gmax_s - 0.069806096) < 0.001,
       PB_var_gmax_s == 0)

@@

Whereas medium to high diversity in only PB led to coexistence of all three functional groups at low oxygen diffusivity levels (Figure \@ref(fig:PB-stabstat4)), presence of only the most tolerant PB strain led to the standard-pattern of either dominance of sulfur bacteria or of cyanobacteria (Figure \@ref(fig:PB-stabstat5)). The most tolerant PB strain has a low maximum growth rate, leading to less consumption of sulfide and therefore to higher sulfide concentrations compared to a system that contains both slow- and fast-growing strains. Due to the higher sulfide concentrations in the system with only the most tolerant PB strain, cyanobacteria were not able to grow at low oxygen diffusivity levels.

For the same reasons we found a similar pattern on the trajectory of increasing oxygen diffusivity for medium to high simultaneous trait variation in PB and CB but not for the corresponding tolerance manipulation (data not shown).

```{r}
wait_time <- "1e+06"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))

max_CB_var_gmax <- max(ss_9s$CB_var_gmax_s)
max_SB_var_gmax <- max(ss_9s$SB_var_gmax_s)
max_PB_var_gmax <- max(ss_9s$PB_var_gmax_s)

ss_9s <- ss_9s %>%
  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
```

(ref:PB-stabstat4) Coexistence of all three groups at low oxygen diffusivities when only PB contains strain variation, and the amount of strain variation is moderate to high. This example is when the standardised amount of trait variation is 0.89 (0 being no variation, and 1 being the maximum amount in any simulation.)

```{r PB-stabstat4, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat4)', fig.height=10, fig.width=8, fig.align="center"}
this_dat <- ss_9s %>%
  filter(
    CB_var_gmax_s == 0,
    SB_var_gmax_s == 0
  )
this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
which_one <- 18
#print(paste0("Standardised level of variation = ",
#round(this_dat$standvar_PB_gmax[this_one],2)))
fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
```

```{r}
wait_time <- "1e+06"
ss_tol <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_-1strains_waittime", wait_time,
                                   "_event_definition_2.RDS")))

max_CB_var_gmax <- max(ss_tol$CB_var_gmax_s)
max_SB_var_gmax <- max(ss_tol$SB_var_gmax_s)
max_PB_var_gmax <- max(ss_tol$PB_var_gmax_s)

ss_tol <- ss_tol %>%
  mutate(standvar_CB_gmax = CB_var_gmax_s / max_CB_var_gmax,
         standvar_SB_gmax = SB_var_gmax_s / max_SB_var_gmax,
         standvar_PB_gmax = PB_var_gmax_s / max_PB_var_gmax)
```

(ref:PB-stabstat5) Dynamics when there is high tolerance in only PB, with this being the same tolerance level as the most tolerant strain in Figure \@ref(fig:PB-stabstat4) immediately above.

```{r PB-stabstat5, echo = FALSE,  include=TRUE, fig.cap='(ref:PB-stabstat5)', fig.height=10, fig.width=8, fig.align="center"}
this_dat <- ss_tol %>%
  filter(
    CB_var_gmax_s == 0,
    SB_var_gmax_s == 0
  )
this_dat <- this_dat[order(this_dat$PB_var_gmax_s), ]
which_one <- 18
#print(paste0("Standardised level of variation = ",
#round(this_dat$standvar_PB_gmax[this_one],2)))
fig_state_vs_o2diff_sidebyside_alternative(this_dat[which_one,])
```

@@

At high levels of diversity / high levels of tolerance, resilience of the oxic state is greater in the tolerance than diversity manipulation. We have shown that low tolerance sulfur strains can be implicated in the oxic to anoxic transition (section \@ref(SB2))
